

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%					NSF requirement, DO NOT ADJUST 							%	
\documentclass[11pt,letterpaper]{article}									%
\usepackage{mathptmx} % added for time new roman font						%
\usepackage[left=1.5in,right=1.5in,top=1in,bottom=1in]{geometry}			%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{placeins}		% Added for \FloatBarrier
\usepackage{enumitem}		% Added for changes in \item
\usepackage{commath} 		% added for \norm
\usepackage{bm}				% added for \bm
\usepackage{wrapfig}
\usepackage{tabu}
\usepackage{float}
\usepackage{booktabs}




\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}		% added for custom .bst file, as explained here. https://tex.stackexchange.com/questions/67444/doi-in-ieeetran-bibliography




\begin{document}

\begin{center}{\Large 
	\textbf{\LaTeX\ file for testing .bst files.}}
\end{center}





	
		
		
		
	\section*{Custom BibTeX format}		

	This BibTeX format is intended for use in NSF submissions. 	Here are some examples of various reference types \cite{test1,test2,test3,test4,test5,test6,test7,test8,test9}.	 A few key items of concern are:
	\begin{itemize}
	\item  This BibTeX format does not use full names (as you can not always get full names on papers).
	\item This BibTeX format is designed to work with Jabref where you use the auto BibTeX generator for a DOI and the arXiv number. However, if there is a URL defined by the BibTeX entry this supersedes the auto-generated URL.
	\item All URLs are hyperlinked, as is the title in the article format
	\item You must use <\textbackslash usepackage[hidelinks]\{hyperref\}> to make links hyperlinks
	\item Underscores ``\_'' in the DOI entry will break the BibTeX compile, you must insert a backslash (e.g., \textbackslash \_) by hand in the .bib file. 
	\item Note that jabref leaves the year blank for a arXiv number. 
	\item The major changes in the .bst file are on line 1923.
	\end{itemize}
		
\pagestyle{empty}
	\FloatBarrier
	%\newpage
	%\pagestyle{empty}
	\renewcommand{\thepage}{}
	\renewcommand\refname{References Cited}
	\bibliographystyle{Downey_NSF} % must use <\usepackage[hidelinks]{hyperref}> for links to be hyperlinks.
	\bibliography{references}

\end{document}


